Hydra Battles and Cie

### 2021-02-10 doc/part-hydras.tex
work on the index

We can make bigger steps through iterations of \texttt{next}.
The functional \texttt{iterate}, similar to Standard Library's \texttt{Nat.iter},
is defined and studied in~\href{../theories/html/hydras.Prelude.Iterates.html\#iterate}{Prelude.Iterates}.

@@

\index{hydras}{Notations!phi0@phi0 (exponential of base omega)}

@@

@@

It is quite easy to prove that our function \texttt{F\_} satisfies the equations on page~\pageref{sect:F-equations}.

@@

@@

@@

\label{Constants:zero:Ord}

@@

\label{Functions:succ-sch}

@@

\index{maths}{Ordinal numbers!Ordering functions}

@@

\begin{Coqsrc}
Definition plus alpha := ord  (ge alpha).
Notation "alpha + beta " := (plus alpha beta) : schutte_scope.
\end{Coqsrc}

@@

\index{maths}{Ordinal numbers!Additive principal ordinals}

@@

\begin{Coqsrc}
Definition phi0 := ord AP.

@@

\index{hydras}{Predicates!Closed}

@@

\index{maths}{Ordinal numbers!Critical ordinals}

@@

>>>>

We can make bigger steps through iterations of \texttt{next}.
The functional \texttt{iterate}, similar to Standard Library's \texttt{Nat.iter},
is defined and studied in~\href{../theories/html/hydras.Prelude.Iterates.html\#iterate}{Prelude.Iterates}.
\index{hydras}{Library Prelude!iterate}

@@

\index{hydras}{Library Epsilon0!Notations!phi0@phi0 (exponential of base omega)}

@@

\index{hydras}{Library Prelude!iterate}
\begin{Coqsrc}
Fixpoint iterate {A:Type}(f : A -> A) (n: nat)(x:A) :=
  match n with
  | 0 => x
  | S p => f (iterate  f p x)
  end.
\end{Coqsrc}

@@

It is quite easy to prove that our function \texttt{F\_} satisfies the equations on page~\pageref{sect:F-equations}.
\index{hydras}{Library Prelude!iterate}

@@

\index{hydras}{Library Schutte!Types!Ord}

@@

\index{hydras}{Library Schutte!Type classes!WO@ WO (well order)}

@@

\label{Constants:zero:Ord}
\index{hydras}{Library Schutte!Constants!zero}

@@

\label{Functions:succ-sch}
\index{hydras}{Library Schutte!Functions!succ}

@@

\index{maths}{Ordinal numbers!Ordering functions}
\index{hydras}{Library Schutte!Predicates!ordering function@ordering\_function}

@@

\index{hydras}{Library Schutte!Functions!plus}
\begin{Coqsrc}
Definition plus alpha := ord  (ge alpha).
Notation "alpha + beta " := (plus alpha beta) : schutte_scope.
\end{Coqsrc}

@@

\index{maths}{Ordinal numbers!Additive principal ordinals}
\index{hydras}{Library Schutte!AP@AP (additive principal ordinals)}

@@

\index{hydras}{Library Schutte!Functions!phi0}
\begin{Coqsrc}
Definition phi0 := ord AP.

@@

\index{hydras}{Library Schutte!Predicates!Closed}

@@

\index{maths}{Ordinal numbers!Critical ordinals}
\index{hydras}{Library Scutte!Cr@Cr (critical ordinals)}

@@

\index{maths}{Ordinal numbers!Cantor normal form}
\index{hydras}{Library Schutte!Predicates!is\_cnf\_of@is\_cnf\_o (to be a Cantor normal form}
